\singlespacing{
\section*{Acknowledgments}

To Neil - thanks for creating a space at MIT for research that doesn't fit wholly within one field.  Thanks for setting up probably one of the best places in the world to make things, and thanks for occasionally letting me use the tools to make things that aren't necessarily research.\\

To my readers Caitlin and Erik - thanks for your time and input and for helping me to ground this work in existing techniques.  I hope that we keep working together.\\

To the CBA students - Sam, Will, Matt, Ben, Eric, Nadya, Prashant, Michael, Noah, Thras, Charles, Lisa, and James - you've all taught me so much.  Thanks for the times we hung out and didn't talk about research too!  Special thanks to Will for all the long conversations about assemblers and helping me to not lose my mind.\\

To everybody that keeps CBA going - Jamie, Ryan, Joe, Sherry, Tom, and John - thanks for all the long chats, antics, dog days, digikey orders, for keeping the shop running smoothly, and for taking me all around the world to do cool stuff.\\

To everybody at E-Line - I've been really enjoying our conversations and the way that our collaboration has been shaping the research.  Thanks for helping me to think about this work from a totally different perspective.\\

To Palash, Jon, Tomer, and Chikara - thanks for the pep talks, dinners, and for help navigating the crit day madness.\\

To everybody at Instructables - thanks for providing the perfect place to experiment and grow after graduating from college.  Special thanks to Dave and Phil for teaching me how to be a real programmer.\\

To Dwight and Phil and the rest of the Pomona Physics Dept - in a lot of ways I feel like this work is an extension of my undergrad thesis.  Thanks for letting me work on projects that didn't seem to fit in a physics department and giving me a safe place to fail.\\

To my Mom, Dad, and Tracey - thanks for always supporting me even though sometimes it's hard to explain what I'm doing.\\

To Michael - thanks for putting up with my terrible work/life balance and helping me through the stress and occasional crying.  Thanks for staying on the phone with me when I walk home at 3am and for listening when I go on and on about the compass. Even though I'm still not that tough, thanks for making me tougher.

}